Think deep for reef resilience

### 2025-08-09 paper/paper_draft.qmd
Fix missing figure references

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and GCM
development families \[**TI: Ben, what does "GCM development families" mean?**\]. The IPCC
defines ECS as the long term warming caused by a doubling of carbon dioxide above its
pre-industrial concentration [@forster2021]. The five GCMs therefore allow for a range of
possible climate futures to be explored, capturing the uncertainty in future responses to
CO2 increases (@fig-ecs; @sfig-methods-dhws; [@grose2023; @shepherd2018]) **\[TI: Missing
figure reference?\]**. Projections using Shared Socio-economic Pathway (SSP) 2-4.5 was used
to represent the plausible emission pathway. It represents a moderate emissions scenario
with continued CO2 emissions comparable to present day until 2050, after which emissions
gradually decline. Under this scenario, atmospheric concentrations approximately reach
540ppm by 2100 [@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to
4.31°C of global atmospheric warming in the 2081-2100 period relative to 1850-1900.

@@

: Information for each GCM used in this investigation including ECS value, interpreted
relative severity and where results are individual GCM results are found. GCMs in context
with assessed plausible ranges of ECS values are displayed in [@sfig-ecs] **\[TI: Missing
figure?\]**. ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS
values, thus results are displayed in the main text. ECS value sources: .
:::

>>>>

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and a range of  GCM
development families \[**TI: Ben, what does "GCM development families" mean?**\]. The IPCC
defines ECS as the long term warming caused by a doubling of carbon dioxide above its
pre-industrial concentration [@forster2021]. The five GCMs therefore allow for a range of
possible climate futures to be explored, capturing the uncertainty in future responses to
CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using Shared Socio-economic Pathway (SSP) 2-4.5 was used
to represent the plausible emission pathway. It represents a moderate emissions scenario
with continued CO2 emissions comparable to present day until 2050, after which emissions
gradually decline. Under this scenario, atmospheric concentrations approximately reach
540ppm by 2100 [@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to
4.31°C of global atmospheric warming in the 2081-2100 period relative to 1850-1900.

@@

: Information for each GCM used in this investigation including ECS value, interpreted
relative severity and where results are individual GCM results are found. GCMs in context
with assessed plausible ranges of ECS values are displayed in [@sfig-ecs]. ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS
values, thus results are displayed in the main text. ECS value sources: .
:::
